---
title: "delete Ticks"
author: "Yury Maisiayonak"
date: "`r Sys.time()`"
output: html_document
params: 
    server: "tt.tt-ag.st.soft-fx.eu"
    login: ""
    password: ""
    symbol: "EURUSD"
    from: "2017-11-09 14:09:30"
    to: "2017-11-09 14:19:30"
---
```{r setup, cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE, tidy = FALSE, results='hide'}
```

```{r cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE, tidy = FALSE, results='hide'}
library(lubridate) 
library(data.table) 
library(foreach) 
library(DT) 
library(plotly) 
library(rFdk)
library(rTTManApi)
options(scipen = 999)
unlink(paste(file.path(), "rFdk", sep = ""), recursive = TRUE)

# getTickAndBarsInfo<-function(server, login, password, symbol, startTime, endTime, depth, barsType = "BidAsk", period = "M1", ){
#   unlink(paste(file.path(), "rFdk", sep = ""), recursive = TRUE)
#   list(bestTicks = ttFeed.TickBestHistory(symbol,startTickCheckTime, endTickCheckTime),
#        ticksL2 = ttFeed.TickLevel2History(symbol,startTickCheckTime, endTickCheckTime,350),
#        bars = ttFeed.BarHistory(symbol,"BidAsk", "M1", startBarCheckTime, endBarCheckTime))
# }


#getting Ticks before deleting

startDeleteTime = as.POSIXct(params$from, tz = "GMT")
endDeleteTime = as.POSIXct(params$to, tz = "GMT")
startTickCheckTime = startDeleteTime-seconds(5)
endTickCheckTime = endDeleteTime+seconds(5)
startBarCheckTime = startDeleteTime-minutes(1)
endBarCheckTime = endDeleteTime+minutes(1)
symbol = params$symbol

ttConnect(params$server, params$login, params$password, fdkPath = paste(file.path(), "rFdk", sep = ""))
oldTicks <- ttFeed.TickBestHistory(symbol,startTickCheckTime, endTickCheckTime)
oldL2Ticks <-ttFeed.TickLevel2History(symbol,startTickCheckTime, endTickCheckTime,350)

deleteTicks <- ttFeed.TickBestHistory(symbol,startDeleteTime, endDeleteTime)
deleteTicksL2 <- ttFeed.TickLevel2History(symbol,startDeleteTime, endDeleteTime, 350)
deleteTicks2 <- deleteTicksL2[level == 1]
oldBars <-ttFeed.BarHistory(symbol,"BidAsk", "M1", startBarCheckTime, endBarCheckTime)
ttDisconnect()

#Delete Ticks
ttmConnect(params$server, params$login, params$password)
ttmDeleteSymbolTicks(symbol, fromTime = startDeleteTime, fromIndex = 0, toTime = endDeleteTime, toIndex = 0)
#Upstream Bars
ttmUpstream(symbol, startBarCheckTime, endBarCheckTime)
ttmDisconnect()

#Getting tmep Ticks, temp Bars and remove previous storage
unlink(paste(file.path(), "rFdk", sep = ""), recursive = TRUE)
ttConnect(params$server, params$login, params$password, fdkPath = paste(file.path(), "rFdk", sep = ""))
tempTicks <- ttFeed.TickBestHistory(symbol,startTickCheckTime, endTickCheckTime)
tempL2Ticks <-ttFeed.TickLevel2History(symbol,startTickCheckTime, endTickCheckTime,350)
tempBars <- ttFeed.BarHistory(symbol,"BidAsk", "M1", startBarCheckTime, endBarCheckTime)
ttDisconnect()

#Insert new Tick and make new Bars
ttmConnect(params$server, params$login, params$password)
ttmInsertLevel2Ticks(symbol, deleteTicksL2$createTime, deleteTicksL2$priceBid, deleteTicksL2$volumeBid, deleteTicksL2$priceAsk, deleteTicksL2$volumeAsk, deleteTicksL2$level)
# ttmInsertTicks(symbol, deleteTicks2$createTime, deleteTicks2$priceBid, deleteTicks2$volumeBid, deleteTicks2$priceAsk, deleteTicks2$volumeAsk)
t1 = ttmUpstream(symbol, startBarCheckTime, endBarCheckTime)
ttmDisconnect()

#Getting new Ticks, new Bars and remove previous storage
unlink(paste(file.path(), "rFdk", sep = ""), recursive = TRUE)
ttConnect(params$server, params$login, params$password, fdkPath = paste(file.path(), "rFdk", sep = ""))
newTicks <- ttFeed.TickBestHistory(symbol,startTickCheckTime, endTickCheckTime)
newL2Ticks <- ttFeed.TickLevel2History(symbol,startTickCheckTime, endTickCheckTime,350)
newBars <- ttFeed.BarHistory(symbol,"BidAsk", "M1", startBarCheckTime, endBarCheckTime)

checkEquivalence<- function(byStreamRequest, byRequest) {
  if(nrow(byStreamRequest) != nrow(byRequest))
    return ("Invalid numbers of row")
  if(!identical(byStreamRequest, byRequest)) {
    for(i in 1: nrow(byStreamRequest)) {
      if(!identical(byStreamRequest[i], byRequest[i])) {
        s = paste("data is not identical in ", toString(i), " see Diagnostic")
        return(c(s, toString(i)))
      }
    }
  }
  return("Data is identical")
}
result = checkEquivalence(oldBars, newBars)
result2 = checkEquivalence(oldTicks, newTicks)
result3 = checkEquivalence(oldL2Ticks, newL2Ticks)
```

###Parameters
Server: _`r params$server`_.

Login: _`r params$login`_.

Password: _`r params$password`_.

Symbol: _`r symbol`_.

Period: _`r startDeleteTime`_ - _`r endDeleteTime`_.

##Old Ticks: 
### _`r startTickCheckTime`_ - _`r endTickCheckTime`_
```{r echo=F}
datatable(oldTicks)
```

##Old Bars: 
### _`r startBarCheckTime`_ - _`r endBarCheckTime`_
```{r echo=F}
datatable(oldBars)
```

##Ticks should be removed: 
### _`r startDeleteTime`_ - _`r endDeleteTime`_
```{r echo=F}
datatable(deleteTicks)
```

##Temp Ticks:  
###_`r startTickCheckTime`_ - _`r endTickCheckTime`_
```{r echo=F}
datatable(tempTicks)
```

##Temp Bars: 
### _`r startBarCheckTime`_ - _`r endBarCheckTime`_
```{r echo=F}
datatable(tempBars)
```

##New Ticks:  
###_`r startTickCheckTime`_ - _`r endTickCheckTime`_
```{r echo=F}
datatable(newTicks)
```

##New Bars: 
### _`r startBarCheckTime`_ - _`r endBarCheckTime`_
```{r echo=F}
datatable(newBars)
```

###Checking deleting
  (oldTick Count - tempTick Count) == deleteTickCount__ **`r nrow(oldTicks)-nrow(tempTicks) == nrow(deleteTicks)`**

###Checking inserting
  (newTick Count - tempTick Count) == deleteTickCount__ **`r nrow(newTicks)-nrow(tempTicks) == nrow(deleteTicks)`**

###Bars checking
  oldBars == newBars__ **`r result`**
  
###Ticks checking
  oldTicks == newTicks__ **`r result2`**

###TicksL2 checking
  oldL2Ticks == newL2Ticks__ **`r result3`**
  
  